---
title: "TL vs FL"
author: "Erin Johnston"
date: "2024-04-13"
output: html_document
---

This script is to run code for total vs fork length taken in mm during the 2023 season.


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

```

```{r libraries}

library(tidyverse)
library(here)

```

```{r data}

raw <- read_csv(here("Data", "2024_CP_Angler_Meeting_2023_SW.csv"))

SW23 <- raw %>%
  filter(year == 2023) %>%
  drop_na(FL_mm, TL_mm) ## 6380 fish with both TL and FL measurements

dat_n <- SW23 %>% count(species) %>% arrange(desc(n))

BLA <- SW23 %>%
  filter(species == "BLA")

BLU <- SW23 %>%
  filter(species == "BLU")

CNY <- SW23 %>%
  filter(species == "CNY")

CPR <- SW23 %>%
  filter(species == "CPR")

DEA <- SW23 %>%
  filter(species == "DEA")

OLV <- SW23 %>%
  filter(species == "OLV")

VER <- SW23 %>%
  filter(species == "VER")

YTL <- SW23 %>%
  filter(species == "YTL")

QBK <- SW23 %>%
  filter(species == "QBK")

```

Black RF - 225
Blue RF - 2068
Canary RF - 113
Copper RF - 102
Deacon RF - 297
Olive RF - 295
Vermilion RF - 264
Yellowtail RF - 97
Quillback RF - 31

```{r function for adding line}

lm_eqn <- function(df){
    m <- lm(TL_mm ~ FL_mm, df);
    eq <- substitute(italic(TL) == b%.%italic(FL) + a*","~~italic(r)^2~"="~r2*, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

num_ind <- function(df){
  test <- df %>% count()
  num <- test$n
  num_eq <- paste0("n = ", num)
  as.character(as.expression(num_eq))
}
```


### Black Rockfish

```{r}

mod_BLA <- lm(TL_mm ~ FL_mm, data = BLA)
summary(mod_BLA)
sigma(mod_BLA)

BLA_lm_plot <- ggplot(data = BLA, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Black Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())


BLA_lm_plot_eq <- BLA_lm_plot + geom_text(x = 200, y = 400, label = lm_eqn(BLA), parse = TRUE, size = 7)+ geom_text(x = 200, y = 300, label = num_ind(BLA), size = 7)

```
### Blue Rockfish

```{r}

mod_BLU <- lm(TL_mm ~ FL_mm, data = BLU)
summary(mod_BLU)
sigma(mod_BLU)

BLU_lm_plot <- ggplot(data = BLU, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Blue Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

BLU_lm_plot_eq <- BLU_lm_plot + geom_text(x = 174, y = 400, label = lm_eqn(BLU), parse = TRUE, size = 7)+ geom_text(x = 175, y = 300, label = num_ind(BLU), size = 7)


```

### Canary Rockfish

```{r}

mod_CNY <- lm(TL_mm ~ FL_mm, data = CNY)
summary(mod_CNY)
sigma(mod_CNY)

CNY_lm_plot <- ggplot(data = CNY, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Canary Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

CNY_lm_plot_eq <- CNY_lm_plot + geom_text(x = 275, y = 400, label = lm_eqn(CNY), parse = TRUE)


```

### Copper Rockfish

```{r}

mod_CPR <- lm(TL_mm ~ FL_mm, data = CPR)
summary(mod_CPR)
sigma(mod_CPR)

CPR_lm_plot <- ggplot(data = CPR, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Copper Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

CPR_lm_plot_eq <- CPR_lm_plot + geom_text(x = 325, y = 450, label = lm_eqn(CPR), parse = TRUE)


```

### Deacon Rockfish

```{r}

mod_DEA <- lm(TL_mm ~ FL_mm, data = DEA)
summary(mod_DEA)
sigma(mod_DEA)

DEA_lm_plot <- ggplot(data = DEA, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Deacon Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

DEA_lm_plot_eq <- DEA_lm_plot + geom_text(x = 200, y = 400, label = lm_eqn(DEA), parse = TRUE)


```

### Olive Rockfish

```{r}

mod_OLV <- lm(TL_mm ~ FL_mm, data = OLV)
summary(mod_OLV)
sigma(mod_OLV)

OLV_lm_plot <- ggplot(data = OLV, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Olive Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

OLV_lm_plot_eq <- OLV_lm_plot + geom_text(x = 230, y = 400, label = lm_eqn(OLV), parse = TRUE)


```

### Vermilion Rockfish

```{r}

mod_VER <- lm(TL_mm ~ FL_mm, data = VER)
summary(mod_VER)
sigma(mod_VER)

VER_lm_plot <- ggplot(data = VER, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Vermilion Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

VER_lm_plot_eq <- VER_lm_plot + geom_text(x = 200, y = 400, label = lm_eqn(VER), parse = TRUE)


```

### Yellowtail Rockfish

```{r}

mod_YTL <- lm(TL_mm ~ FL_mm, data = YTL)
summary(mod_YTL)
sigma(mod_YTL)

YTL_lm_plot <- ggplot(data = YTL, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Yellowtail Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

YTL_lm_plot_eq <- YTL_lm_plot + geom_text(x = 200, y = 400, label = lm_eqn(YTL), parse = TRUE)


```

### Quillback Rockfish

```{r}

mod_QBK <- lm(TL_mm ~ FL_mm, data = QBK)
summary(mod_QBK)
sigma(mod_QBK)

QBK_lm_plot <- ggplot(data = QBK, aes(x = FL_mm, y = TL_mm))+
  geom_point()+
  geom_smooth()+
  labs(x = "Fork Length (mm)", y = "Total Length (mm)\n", title = "Quillback Rockfish")+
  theme_bw()+
  theme(panel.grid = element_blank())

QBK_lm_plot_eq <- QBK_lm_plot + geom_text(x = 200, y = 400, label = lm_eqn(QBK), parse = TRUE)


```

Black RF - 225
Blue RF - 2068
Canary RF - 113
Copper RF - 102
Deacon RF - 297
Olive RF - 295
Vermilion RF - 264
Yellowtail RF - 97
Quillback RF - 31
```{r saving plots}


ggsave("BLA_lm_plot_eq.png", plot = BLA_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("BLU_lm_plot_eq.png", plot = BLU_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("CNY_lm_plot_eq.png", plot = CNY_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("CPR_lm_plot_eq.png", plot = CPR_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("DEA_lm_plot_eq.png", plot = DEA_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("OLV_lm_plot_eq.png", plot = OLV_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("VER_lm_plot_eq.png", plot = VER_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("YTL_lm_plot_eq.png", plot = YTL_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)
ggsave("QBK_lm_plot_eq.png", plot = QBK_lm_plot_eq, path = here("Figures"), dpi = 800, height = 5, width = 7)

```

